---
title: "My Storyboard at DACSS - frames"
bibliography: testVisual.bib
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Intro {.sidebar}

Preparing the dashboard based on the instructions given at @magallanes_reyes_data_2022, and @aden-buie_flexdashboard_2026.



### I know this is not nice, but wait till I finish the course


```{r}
## for del1Draft.rds
link1="https://github.com/DACSS-690V-SP26/hw-test/raw/main/del1Draft.rds"
readRDS(url(link1))
```



### I am doing my best but still much to learn

```{r}
## for del2Draft.rds
link2="https://github.com/DACSS-690V-SP26/hw-test/raw/main/del2Draft.rds"
readRDS(url(link2))
```


### This might be the worst plot, but...

```{r}
## for del3Draft.rds
link3="https://github.com/DACSS-690V-SP26/hw-test/raw/main/del3Draft.rds"
readRDS(url(link3))
```


### References


# HW2 

## HW2 Instructions  {.sidebar}

Replicating plots from Main Tools lecture. 

### Loading the data 

```{r}
mtcars
library(ggplot2)
```

### Plot 1: Three-Gear Cars are Dominant 
```{r}
mtcars_cyl=mtcars$cyl|>table()|>as.data.frame()
plot2= ggplot(mtcars_cyl, aes(x=factor(Var1), y=Freq, label=Freq)) +
  geom_bar(stat = 'identity', fill = "lightgrey") +
  geom_text(hjust=2,size=10, color='blue',fontface = "bold") + coord_flip() + labs(x='Gear', title = 'Count of Cars per GEAR', caption = "Source: mtcars data") + theme_classic() + theme(axis.title.x = element_blank(), axis.line.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
plot2
```
